Instructions for COLING-2020 Proceedings

### 2020-06-26 Paper/main.tex
Commit for pdf

\documentclass[11pt]{article}

@@

\section{Introduction}
\label{sec:intro}

@@

\section{Related Work}
\label{sec:related}

\subsection{Ben}

Very similar to what we want to do: \cite{rupnik2016news,miranda2018multilingual,wang2018estimation,germann2019scalable,seki2018exploring,seki2020cross,linger2020batch}

Brexit case study: \cite{peterlin2019detecting}

Also similar, but involving search terms; probably just good for citations and not techniques: \cite{rupnik2016news}

Multilingual BERT:

\cite{K2020Cross-Lingual}

\cite{pires2019multilingual}

More multilingual models non-BERT from google:

https://ai.googleblog.com/2019/07/multilingual-universal-sentence-encoder.html

https://arxiv.org/abs/1807.11906
https://arxiv.org/abs/1810.12836
https://arxiv.org/abs/1902.08564
https://arxiv.org/abs/1906.08401
https://arxiv.org/abs/1907.04307

Old survey but good on non deep learning techniques of the era: \cite{oard1998survey}.

\subsection{Stefanos}

Datasets:

\cite{liu2019dens}

\cite{SemEval2018Task1}

@@

\cite{puri2018large}

\cite{kant2018practical}

@@

\cite{mohammad2015sentiment}

\cite{hemmatian2017survey}

\cite{yang2015twitter}

\subsection{Nate}

Look at the way these papers run experiments:

\cite{tifrea2018poincar,meng2019spherical}

Datasets at: \url{https://aclweb.org/aclwiki/Similarity_(State_of_the_art)}

Use wikidata to automatically generate classes: https://www.wikidata.org/wiki/Q43689 
https://pywikidata.readthedocs.io/en/latest/

wikidata church fathers in latin: \url{https://query.wikidata.org/#SELECT%20%3Fperson%20%3FpersonLabel%0AWHERE%20%7B%0A%20%20%3Fperson%20wdt%3AP361%20wd%3AQ182603.%0A%20%20SERVICE%20wikibase%3Alabel%20%7B%20bd%3AserviceParam%20wikibase%3Alanguage%20%22la%22.%20%7D%0A%7D}

SPARQL Tutorial: https://www.wikidata.org/wiki/Wikidata:SPARQL_tutorial

Can we use wikidata to automatically generate good evaluations?

>>>>

\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{enumitem}

@@

\section{Introduction}
\label{sec:intro}
\begin{center}
\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{images/finalcountgraph1.eps}
  \caption{Number of tweets per day...}
  \label{fig:1}
\end{figure}
\end{center}
\newpage

@@

\subsection{Plutchik's Wheel of Emotions}

\begin{figure}[!ht]
    \includegraphics[width=0.4\textwidth]{images/Plutchik-wheel.png}
    \caption{Plutchik's emotion wheel}
    \label{fig:2}
    \includegraphics[width=\textwidth]{images/emotions.eps}
    \caption{Results of sentiment analysis conducted using nvidia-sentiment on 170k tweets related with the corona outrbreak }
    \label{fig:3}
\end{figure}
\newpage

\section{Related Work}
\label{sec:related}
\subsection{Stefanos}
Datasets: 
\begin{enumarate}
  \item DENS: A Dataset for Multi-class Emotion Analysis:By finetuning the pre-trained uncased BERT-large to a multi-class passage classification task they achieved a micro-F1 score of 60.4\%. 
  \item 
\end{enumarate}

%\cite{liu2019dens}

%\cite{SemEval2018Task1}

@@

%\cite{puri2018large}

%\cite{kant2018practical}

@@

%\cite{mohammad2015sentiment}

%\cite{hemmatian2017survey}

%\cite{yang2015twitter}
